### 2015-01-23 paper_20_sdo.tex
updated the PDF output file

    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

            ``
                A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results.
            '' as quoted from
            \cite{Jones2009}.  Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
\end{description}

>>>>

    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] ``A software defect is a bug or error that causes
                software to either stop operating or to produce
                invalid or unacceptable results'' as quoted from
            \cite{Jones2009}.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

              Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
\end{description}
